Abstraction-averse programming

### 2024-02-22 latex/ms.tex
.

\title{Software Development Methodology}

@@

\begin{abstract}
	We propose a portable and consistent software development methodology and also refer to example use cases.
\end{abstract}

\section{Introduction}
Code is usually targeted to be executed by multiple machines and developed by multiple humans.
Therefore, it is vital to have a portable way for machines to execute code and a consistent way for humans to develop code.
In this paper we present a simple software development methodology which satisfies these conditions.
We propose using POSIX XCU and Containers for code portability and a directory structure enforcement for code consistency.
We also refer example use cases for python machine learning applications, \LaTeX{} documents generation and web applications.

>>>>

\title{Abstraction-averse programming}

@@

\begin{abstract}
	We propose a software development methodology for portable and consistent code and also refer to example use cases.
\end{abstract}

\section{Introduction}
The most important problem today with software is its increasing complexity which can be attributed to the use of unnessesary abstractions.
Abstractions can be variables, functions, classes, modules, files, directories, third-party dependencies.
Most of the times using already existing abstractions is better than creating/introducing new ones.

Code is usually targeted to be executed by multiple machines and developed by multiple humans.
Therefore, it is vital to have a portable way for machines to execute code and a consistent way for humans to develop code.
In this paper we present a simple software development methodology which satisfies these conditions.
We propose using POSIX XCU and Containers for code portability and a directory structure enforcement for code consistency.
We also refer example use cases for python machine learning applications, \LaTeX{} documents generation, web applications and python packages.

\section{Abstraction-averse programming}
The phrase "Abstraction-averse" is in contrast to "Abstraction-free" where would need to program in machine language (0s and 1s) exactly as the CPU sees them.
However "Abstraction-averse" recognizes the practical aspect of abstraction but instructs that the introduction/creation of abstractions should be avoided as much as possible.
